A Fully Decentralized Infrastructure for Subscription-based IoT Data Trading

### 2020-07-15 paper.tex
Refactor Chap 3 smart contract

\subsection{Enable Automated Trading Process}
\begin{figure}[h]
    \centering
    \includegraphics[width=3.5in]{smart_contract_mam_shrink}
    \caption{The information of identity and data streams are stored on the Tangle with MAM which are all recorded on Product Contracts. Participants can easily retrieve information via Product Contract and proceed trading. For signature validation check and further exchange encryption keys, the MAM channel ID of participants' DID document  are written down, presented in blue color. The orange color stands for the information of data products, which includes the data stream channel/endpoint ID and encryption key certified by broker.}
    \label{fig:smart_contract_mam}
\end{figure}

Ethereum is a cryptocurrency building on top of a public blockchain-based distributed ledger. It provides the smart contract, which is a protocol for formulating agreement on a blockchain that running on decentralized virtual machines. A smart contract can interact with other contracts, make decisions, store data and transfer cryptocurrency. All the participants in Ethereum can verify and execute the contracts, and once the contract is triggered, it is uninterruptible and will be executed automatically without any third-parties.

With the functionalities of Ethereum smart contracts, a flexible and verifiable trading mechanism can be achieved. In our system, \textbf{Product Contract} is made for the product launching and trading. The information of data products such as address of the data provider, subscription fee, brokerage fee, threshold of consent votes of refunding, MAM channel/endpoint ID (the data entry point), time period and the broker-verified encryption key are listed on Product Contract. Fig.~\ref{fig:smart_contract_mam} shows the relationship of Product Contract and MAM. Furthermore, the participants can exchange encryption keys without any authorities via smart contracts. Though this design may cost extra transaction fees than exchanging key off-chain, it is considered a more secure strategy to protect the privacy of participants.

The transparency of smart contracts bring advantages for data providers and consumers. One of the advantage is that the trading states and progress are visible and verifiable which profits providers and consumers respectively. For data providers, with every details opened, the consumer list functions like a reputation evaluation, the better the quality the more the consumers he/her has. The consumer list and the states of products are key reputation referenced for data consumers to decide whether to subscribe.

>>>>

\subsection{Enable Automated Trading Process}
Ethereum is a cryptocurrency building on top of a public blockchain-based distributed ledger. It provides the smart contract that can make decisions, store data and transfer cryptocurrency. All the participants in Ethereum can verify and execute the contracts, and once the contract is triggered, it is uninterruptible and will be executed automatically without any third-parties.

With the functionalities of Ethereum smart contracts, a flexible and verifiable trading mechanism can be achieved. In our system, \textbf{Product Contract} is made for the product launching and trading. The information of data products such as address and DID document address of the data provider, subscription and brokerage fee, MAM channel/endpoint ID (the data entry point), and the broker-certified encryption key are listed on Product Contract. Furthermore, the participants can exchange encryption keys without any authorities via smart contracts. Though this design may cost extra transaction fees than exchanging key off-chain, participants only need to reveal the minimum information containing an Ethereum address and the DID document address to progress.

The transparency of smart contracts bring advantages for data providers and consumers. One of the advantage is that the trading states and progress are visible and verifiable which profits providers and consumers respectively. Preserving a consumer list on Product Contract functions like the reputation of the product, the better the quality the more the consumers he/her has, which are key references for data consumers to decide whether to subscribe.
